Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-01-22 draft.tex
Add comment on comparison of uncertainties with ML fits

Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
        of any observables $S$,
        \begin{equation}
            \mathrm{pull_i} \equiv \frac{\est{S} - S}{\est{\sigma}_S}\,.
        \end{equation}
        Here $S$ refers to the true (input) value for the angular observables, $\est{S}$ refers to the
        MC estimate, and $\est{\sigma} \equiv \sqrt{\est{\Sigma}}$ refers to an estimator of the
        variance of the measurement. All pull distributions obtained in our studies can be successfully
        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
        decays, are good examples. We show their respective pull distributions for \danny{$XXX$} toy studies
        of $200$ events per study in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \label{eq:unc-on-mean}
            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
\end{itemize}
All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
observables converges rapidly towards a multivariate Gaussian distribution. We therefore propose to describe the
resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.

>>>>

Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
        of any observables $S$,
        \begin{equation}
            \mathrm{pull_i} \equiv \frac{\est{S} - S}{\est{\sigma}_S}\,.
        \end{equation}
        Here $S$ refers to the true (input) value for the angular observables, $\est{S}$ refers to the
        MC estimate, and $\est{\sigma} \equiv \sqrt{\est{\Sigma}}$ refers to an estimator of the
        variance of the measurement. All pull distributions obtained in our studies can be successfully
        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
        decays, are good examples. We show their respective pull distributions for \danny{$XXX$} toy studies
        of $200$ events per study in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \label{eq:unc-on-mean}
            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
        We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
        \danny{$10\%$} larger than those obtained from maximum-likelihood fits and with the same
        number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
        subset of the angular observables, and the statistical error of the fit is expected to increase
        with the number of fit parameters \danny{[cite?]}.
    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
\end{itemize}
All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
observables converges rapidly towards a multivariate Gaussian distribution. We therefore propose to describe the
resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.
